Confidence validity of bootstrap regression estimates

### 2020-12-03 gerko/BootstrapCI_Validity.Rmd
updated text to serve in MLaRPiS course

---
title: "Confidence validity of bootstrap estimates"
author: "Gerko Vink"
date: "7/20/2020"
output: 
  html_document:
    toc: true
    toc_depth: 5
    toc_float: true
    number_sections: true
---

@@

# Draw the bootstrap sets
We use the `replicate()` function to draw `nsim =``r nsim` bootstrap sets from the `origin`
```{r cache=TRUE}
simdata <- replicate(nsim, 
                     origin[sample(1:748, 748, replace = TRUE), ], 
                     simplify = FALSE)
```

@@

# Results
Below are the coverages for each of the investigated scenarios. Results are depicted for the coverage of the confidence intervals over the regression estimates for `r nsim` simulations.
```{r}
output <- rbind(colMeans(cov), 
                colMeans(manual), 
                colMeans(manual2), 
                colMeans(cbind(covint$cov, covhgt$cov, covage$cov)))
rownames(output) <- c("confint", 
                      "manual", 
                      "bootstrap SE", 
                      "bootstrap CI")
kable(output, "html") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"),
                full_width = F)
```

@@

>>>>

---
title: "Confidence validity of bootstrap regression estimates"
author: "Gerko Vink"
date: "Markup Languages and Reproducible Programming in Statistics"
output: 
  html_document:
    toc: true
    toc_depth: 5
    toc_float: true
    number_sections: true
---

@@

# Draw the bootstrap sets
We use the `replicate()` function to draw `nsim =`$10^4$ bootstrap sets from the 748 rows in the `origin`.
```{r cache=TRUE}
simdata <- replicate(nsim, 
                     origin[sample(1:748, 748, replace = TRUE), ], 
                     simplify = FALSE)
```

@@

# Results
Below are the coverages for each of the investigated scenarios. Results are depicted for the coverage of the confidence intervals over the regression estimates for $10^4$ simulations.
```{r}
output <- rbind(colMeans(cov), 
                colMeans(manual), 
                colMeans(manual2), 
                colMeans(cbind(covint$cov, covhgt$cov, covage$cov)))
rownames(output) <- c("confint", 
                      "manual", 
                      "bootstrap SE", 
                      "bootstrap CI")
kable(output, "html") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"),
                full_width = F)
```

# Replication
The replication of these results [can be found here]()

@@

```{r}
sessionInfo()
```
